Case Study (McKenna)

### 2020-09-30 Cases/mrp/Case Study (McKenna) .Rmd
working with altering group amts

```{r, eval = FALSE}
# I set this to eval = FALSE just for now because it wasn't knitting so I will have to come back and take a look at this.
options(mc.cores = parallel::detectCores()) # Set Stan to use all available cores.
rstan_options(auto_write = TRUE)            # Don't recompile Stan code that hasn't changed.

@@

```{r}
# Importing the data. 
sample <- read_csv(here::here("Data", "sample.csv"))
poststrat <- read_csv(here::here( "Data", "poststrat.csv"))
true_popn <- read_csv(here::here( "Data", "true_popn.csv"))

@@

Our first model is a hierarchical logit model. A logit model is appropriate for our data because of the biniary outcome variable. The hierarchical model is group baised on the group assignments determined by the categorical variables in the data.

@@

```{r, eval = FALSE}
fit <- stan(
  file = here::here("Code", "mrp", "logit_hier.stan"),
  data = data_list,
  seed = 42 
)
```
```{r, eval = FALSE}
# I think we will need to use a for loop like they do in the downes model to construct our predictions into a format that we can then postratify them. I got this for loop from the downes code and I have just begun to adjust it for our model. 
 n_sim <- (n_iter * n_chain)/2   # They set the chains in their code but I don't think we did for our model so we'll have to take a look and see how to convert this 
n_pscell <- length(poststrat$N) # (n_pscell is the number of poststratification cells defined by the model)
n_state <- max(poststrat$STATE)
stanfit_final_ypred <- array(NA, c(n_sim, n_pscell))

for(l in 1:n_pscell){
    stanfit_final_ypred[,l] <- bernoulli_logit((x[n,] * beta[ll[n]])  # This is the part I am confused the most on. Just trying to specify the model in the right way to be able to make the service failure assumptions to then postratify. 
                                        )

@@

  int<lower=0,upper=n_age> age[n];                    // These are the variables containing
  int<lower=0,upper=n_eth> eth[n];                    // the observed data for each
  int<lower=0,upper=n_income> income[n];              // poststratification factor in the 
  int<lower=0,upper=n_male> male[n];                  // final model
  int<lower=0,upper=n_state> state[n];      
 }
parameters {                                          // Model parameters to be estimated:
  real b0;                                            // "intercept"
  real a_age[n_age];                                  // age varying coeffs (depart from linear fit)
  real a_eth[n_eth];                                  // ethnicity class varying coeffs 
  real a_income[n_income];                            // income varying coeffs (depart linear fit)
  real a_male[n_male];                                // gender varying coeffs
  real a_state[n_state];                              // state varying coeffs
  real<lower=0> sigma_age;                            // age var(sd) component
  real<lower=0> sigma_eth;                            // ethnicit var(sd) component
  real<lower=0> sigma_income;                         // income var(sd) component
  real<lower=0> sigma_male;                           // gender fluency var(sd) component
  real<lower=0> sigma_state;                          // state var(sd) component
}
// transformed parameters {                              // Model specification is here
//   vector[n] outcome_hat;
//   for (i in 1:n) {
//    outcome_hat[i] = b0 + a_age[age[i]] + a_eth[eth[i]] + a_income[income[i]] + a_male[male[i]] + a_state[state[i]];
//   }
// }
model {                                              // Model distributions for varying coefficients
  b0 ~ cauchy(0,2.5);                                // and prior distributions for unmodelled                                                                // Can modify Cauchy scale parameter
                                                     // Can also specify a uniform distribution here
  a_age ~ normal(0, sigma_age);                      // or by setting upper and lower limits for
  a_eth ~ normal(0, sigma_eth);                      // unmodelled parameters in the parameter step
  a_income ~ normal(0, sigma_income);                // above  
  a_male ~ normal(0, sigma_male);                      
  a_state ~ normal(0, sigma_state);

@@

//  outcome ~ bernoulli_logit(outcome_hat);            // For a continuous outcome, specify a
                                                     // normal distribution with an additional
                                                     // variance component, i.e.
                                                     // outcome ~ normal(outcome_hat, sigma_outcome)
                                                     // Note the prior distributions for 
                                                     // unmodelled parameters will change.
}
```

@@

Post-stratification consists of taking the sum of the estimates of the model for each cell times the number of people in each cell divided by the total number of people. Using post-stratificatio ncan improve accuracy of the estimates based on the information known.

>>>>

```{r, eval = FALSE}
options(mc.cores = parallel::detectCores()) # Set Stan to use all available cores.
rstan_options(auto_write = TRUE)            # Don't recompile Stan code that hasn't changed.

@@

```{r}
# Importing the data, will see it exported in environment 
sample <- read_csv(here::here("Data", "sample.csv"))
poststrat <- read_csv(here::here( "Data", "poststrat.csv"))
true_popn <- read_csv(here::here( "Data", "true_popn.csv"))

@@

Our first model is a hierarchical logit model. A logit model is appropriate for our data because of the binary outcome variable. The hierarchical model is group based on the group assignments determined by the categorical variables in the data.

@@

```{r, eval = FALSE}
fit <- stan(
  file = here::here("Code", "mrp", "logit_hier.stan"),
  data = data_list,
  seed = 42 
)
```

```{r, eval = FALSE}
# I think we will need to use a for loop like they do in the downes model to construct our predictions into a format that we can then post-stratify them. I got this for loop from the downes code and I have just begun to adjust it for our model. 
 n_sim <- (n_iter * n_chain)/2   # They set the chains in their code but I don't think we did for our model so we'll have to take a look and see how to convert this 
n_pscell <- length(poststrat$N) # (n_pscell is the number of post-stratification cells defined by the model)
n_state <- max(poststrat$STATE)
stanfit_final_ypred <- array(NA, c(n_sim, n_pscell))

for(l in 1:n_pscell){
    stanfit_final_ypred[,l] <- bernoulli_logit((x[n,] * beta[ll[n]])  # This is the part I am confused the most on. Just trying to specify the model in the right way to be able to make the service failure assumptions to then post-stratify. 
                                        )

@@

  int<lower=0,upper=n_age> age[n];                    // These are the variables containing
  int<lower=0,upper=n_eth> eth[n];                    // the observed data for each
  int<lower=0,upper=n_income> income[n];              // poststratification factor in the 
  int<lower=0,upper=n_male> male[n];                  // final model
  int<lower=0,upper=n_state> state[n];      
 }
parameters {                                          // Model parameters to be estimated:
  real b0;                                            // "intercept"
  real a_age[n_age];                                  // age varying coeffs (depart from linear fit)
  real a_eth[n_eth];                                  // ethnicity class varying coeffs 
  real a_income[n_income];                            // income varying coeffs (depart linear fit)
  real a_male[n_male];                                // gender varying coeffs
  real a_state[n_state];                              // state varying coeffs
  real<lower=0> sigma_age;                            // age var(sd) component
  real<lower=0> sigma_eth;                            // ethnicit var(sd) component
  real<lower=0> sigma_income;                         // income var(sd) component
  real<lower=0> sigma_male;                           // gender fluency var(sd) component
  real<lower=0> sigma_state;                          // state var(sd) component
}
// transformed parameters {                              // Model specification is here
//   vector[n] outcome_hat;
//   for (i in 1:n) {
//    outcome_hat[i] = b0 + a_age[age[i]] + a_eth[eth[i]] + a_income[income[i]] + a_male[male[i]] + a_state[state[i]];
//   }
// }
model {                                              // Model distributions for varying coefficients
  b0 ~ cauchy(0,2.5);                                // and prior distributions for unmodeled                                                                // Can modify Cauchy scale parameter
                                                     // Can also specify a uniform distribution here
  a_age ~ normal(0, sigma_age);                      // or by setting upper and lower limits for
  a_eth ~ normal(0, sigma_eth);                      // unmodeled parameters in the parameter step
  a_income ~ normal(0, sigma_income);                // above  
  a_male ~ normal(0, sigma_male);                      
  a_state ~ normal(0, sigma_state);

@@

//  outcome ~ bernoulli_logit(outcome_hat);            // For a continuous outcome, specify a
                                                     // normal distribution with an additional
                                                     // variance component, i.e.
                                                     // outcome ~ normal(outcome_hat, sigma_outcome)
                                                     // Note the prior distributions for 
                                                     // unmodeled parameters will change.
}
```

@@

Post-stratification consists of taking the sum of the estimates of the model for each cell times the number of people in each cell divided by the total number of people. Using post-stratification can improve accuracy of the estimates based on the information known.
